A generalized definition of multidimensional item response theory parameters

### 2024-03-28 output/paper_draft/paper_M2PLM_parameters.Rmd
Expresses "Test space" section start more formally

Consider now the M2PL model formulation given by Equation
\@ref(eq:M2PL-formulation), on one hand, and Equation \@ref(eq:change-basis) on
the other.
Since the response probability must be invariant with respect to
a change of basis,
we must define the coordinates $`r DISCR_STD_COORDS`$ of the parameter vector
$`r DISCR_VECTOR`$ in an orthonormal basis $`r TEST_SPACE_STD_BASIS`$,
such that $`r INVARIANCE_EQ`$.
If we assume that $`r DISCR_VECTOR`$ exists in vector space $`r TEST_SPACE`$,
with coordinates $`r DISCR_COORDS`$ in basis $`r TEST_SPACE_BASIS`$,
then we must define $`r DISCR_COORDS`$ such that

>>>>

Let $`r TEST_SPACE`$ be the vector space made up by
the set of $`r DISCR_VECTOR`$ vectors,
with the sum and product by a scalar operations as in $`r REAL_N_SPACE`$.
Consider also an orthonormal basis $`r TEST_SPACE_STD_BASIS`$
in $`r TEST_SPACE`$, such that $`r DISCR_STD_COORDS_ALT_EQ`$.
<!-- #TODO: Continue here -->
Since the response probability must be invariant with respect to
a change of basis,
we must define the coordinates $`r DISCR_STD_COORDS`$ of the parameter vector
$`r DISCR_VECTOR`$ in an orthonormal basis $`r TEST_SPACE_STD_BASIS`$,
such that $`r INVARIANCE_EQ`$.
If we assume that $`r DISCR_VECTOR`$ exists in vector space $`r TEST_SPACE`$,
with coordinates $`r DISCR_COORDS`$ in basis $`r TEST_SPACE_BASIS`$,
then we must define $`r DISCR_COORDS`$ such that
